%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Himanshu Singh} \\ \vspace{5pt}
    \small \faPhone* \hspace{2pt}\href{tel:+919585719381}{\myuline{+91 9585719381}} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt}\href{mailto:singhhimanshu004@gmail.com}{\myuline{singhhimanshu004@gmail.com}} \hspace{1pt} $|$
    \hspace{1pt} \faLinkedin \hspace{2pt}\href{https://www.linkedin.com/in/singhhimanshu004/}{\myuline{singhhimanshu004}} \hspace{1pt} $|$
    \hspace{1pt} \faGithub \hspace{2pt}\href{https://github.com/singhhimanshu004}{\myuline{singhhimanshu004}}
    \\ \vspace{2pt}
    \faMapMarker* \hspace{2pt}\texttt{Noida, India}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Microsoft IDC}{Jan 2025 -- Present}
      {Senior Software Engineer}{Noida, India}
      \resumeItemListStart
        \resumeItem{Built self-service provisioning for secured, ephemeral, tenant-isolated sandboxes used by security researchers for malware analysis and security research; reduced environment setup from several hours to \textbf{under 30 minutes}.}
        \resumeItem{Strengthened research-platform isolation by building sandbox lifecycle management, access boundaries and workload separation, keeping research environments isolated from Microsoft dev and prod tenants.}
        \resumeItem{Remediated \textbf{30+ S360} security and compliance findings across infrastructure, dependencies, configuration and deployment pipelines.}
        \resumeItem{Reduced manual infrastructure delivery effort by \textbf{~50\%} by standardizing automation using Terraform, Bicep, ARM JSON, Python, Shell and C\#.}
        \resumeItem{Standardized secured multicloud Kubernetes cluster delivery by building reusable templates for node-pool segmentation, network topology, workload-identity (WIF) pool separation and pre-built observability components (metrics, logs); delivered the first production cluster for a customer and made further cluster creation repeatable.}
        \resumeItem{Baked observability into the cluster template --- dashboards, alerts and health checks --- to support reliability and availability targets for customer workloads.}
        \resumeItem{Leveraged Generative AI and agentic AI to accelerate platform engineering tasks such as code generation, IaC review, test scaffolding and runbook automation; reduced implementation time for repeatable work by \textbf{~45\%}.}
        \resumeItem{Built AI-assisted security triage and validation loops for S360 remediation and infra changes, moving fixes from investigation to reviewed changes \textbf{2--3x faster}.}
      \resumeItemListEnd

    \resumeSubheading
      {JP Morgan Chase}{Jan 2024 -- Dec 2024}
      {Lead Software Engineer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Played a major role in facilitating Sybase exit for legacy applications by creating robust pipelines for Debezium CDC connectors.}
        \resumeItem{Facilitated data movement to AWS PostgreSQL using JDBC connectors by creating custom config providers to support JPMC-specific authentication mechanisms.}
      \resumeItemListEnd

    \resumeSubheading
      {JP Morgan Chase}{Jan 2022 -- Dec 2023}
      {Software Engineer III}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Increased adoption of AWS MSK by \textbf{30\%} in firm by creating fully managed replication service for migrating data from on-prem clusters to MSK.}
        \resumeItem{Reduced time taken to migrate to new datacenter clusters from \textbf{15 days to 1 hour} by creating fully automated namespace migration pipeline.}
        \resumeItem{Coordinated with other engineers to evaluate and improve software and hardware interfaces.}
        \resumeItem{Reviewed project specifications and designed technology solutions that met or exceeded performance expectations.}
        \resumeItem{Worked with software development and testing team members to design and develop robust solutions to meet client requirements for functionality, scalability, and performance.}
      \resumeItemListEnd

    \resumeSubheading
      {JP Morgan Chase}{Jan 2021 -- Dec 2021}
      {Software Engineer II}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Reduced time and resource utilization for data source migration by \textbf{80\%} by creating Kafka Connect Control Plane supporting 30+ source and sink connectors.}
        \resumeItem{Created orchestrator micro-service for building, patching and maintenance of Kafka clusters; brought down time taken to build and patch Kafka cluster from \textbf{2 days to 2 hours}.}
        \resumeItem{Developed robust, scalable, modular and API-centric infrastructures.}
        \resumeItem{Promoted experience with Kubernetes, Docker and Amazon Web Services.}
        \resumeItem{Represented software applications engineering team during large and complex development projects.}
        \resumeItem{Collaborated with clients to define solution requirements.}
        \resumeItem{Informed internal personnel and external stakeholders of project milestones.}
      \resumeItemListEnd

    \resumeSubheading
      {JP Morgan Chase}{Jul 2017 -- Dec 2020}
      {Associate}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Created monitoring framework to do canary health checks on Apache Kafka clusters which generates a real-time cluster health index --- currently used by over \textbf{12,000 applications} using Kafka for failover to DR cluster.}
        \resumeItem{Created pipeline for automatic certificate renewal of hosts owned for Kafka clusters; significantly reduced manual time to create and renew certs from \textbf{1 day to 5 minutes}; currently over \textbf{1,500 certs} for Linux hosts get renewed through this.}
        \resumeItem{Conducted product demonstrations to highlight features and redirect objections to positive aspects.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {VIT University}{Jul 2013 -- Jun 2017}
      {B.Tech in Computer Science}{Vellore, India}
      \resumeItemListStart
        \resumeItem{Cum. GPA: 8.66 / 10.0}
      \resumeItemListEnd

    \resumeSubheading
      {Central Hindu Boys School}{2012}
      {Schooling}{Varanasi, India}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Programming Languages} {: Python, Java, C\#, Shell, JavaScript, TypeScript, Angular}\vspace{2pt} \\
     \textbf{Operating Systems} {: Linux, macOS, Windows, Unix}\vspace{2pt} \\
     \textbf{Messaging \& Streaming} {: Kafka, Kafka Connect, Kafka Streams}\vspace{2pt} \\
     \textbf{Cloud \& Containers} {: AWS, GCP, Azure, PCF, Docker, Kubernetes}\vspace{2pt} \\
     \textbf{Infrastructure as Code} {: Terraform, Bicep, ARM JSON}\vspace{2pt} \\
     \textbf{Frameworks} {: FastAPI, Spring Boot, Flask, Angular, AWS Lambda, API Gateway}\vspace{2pt} \\
     \textbf{AI} {: Generative AI, Agentic AI}\vspace{2pt} \\
     \textbf{Databases} {: Oracle, PostgreSQL}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{CERTIFICATIONS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small
    \item HashiCorp Certified Terraform Associate (Dec 2022)
    \item Certified Kubernetes Application Developer (CKAD) (Nov 2022)
    \item AWS Certified Cloud Practitioner (Aug 2022)
 \end{itemize}

%-----------AWARDS-----------
\section{AWARDS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small
    \item APAC CEO Award (Aug 2023)
    \item Reward of Excellence (Jul 2020)
    \item Winner, SEP Hackathon (Jul 2018)
 \end{itemize}

%-------------------------------------------
\end{document}
